Generation of TypeScript Declaration Files from JavaScript Code

### 2019-12-30 ecoop-2020/main.tex
abstract

%TODO mandatory: add short abstract of the document
\begin{abstract}
Developers are starting to write complex and large applications in
TypeScript, a typed dialect of JavaScript. TypeScript applications
integrate JavaScript libraries via typed descriptions of their APIs
called declaration files. These files are available in public
repository DefinitelyTyped.
This repository is maintained manually, which
is error prone and time consuming. Discrepancies between a
declaration file and the JavaScript implementation lead to
incorrect feedback from the TypeScript IDE and thus to incorrect uses
of the underlying JavaScript library.

This work presents \lstinline{dts-generate}, a tool that generates
TypeScript declaration files for JavaScript libraries uploaded to the NPM
registry. It extracts code examples from the documentation written by
the developer, executes the library driven by the examples, gathers
run-time information, and generates a declaration file based on this
information. To evaluate the tool, 244 declaration files were generated and 
compared against the declaration file provided on DefinitelyTyped, the
standard public repository for declaration files. 33 files out of 244 had no differences. 
\end{abstract}

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
Developers are starting to write large and complex applications in
TypeScript, a typed dialect of JavaScript. TypeScript applications
integrate JavaScript libraries via typed descriptions of their APIs
called declaration files. DefinitelyTyped is the standard public
repository for these files.
The repository is maintained manually by volunteers, which
is error prone and time consuming. Discrepancies between a
declaration file and the JavaScript implementation lead to
incorrect feedback from the TypeScript IDE and thus to incorrect uses
of the underlying JavaScript library.

This work presents \lstinline{dts-generate}, a tool that generates
TypeScript declaration files for JavaScript libraries uploaded to the NPM
registry. It extracts code examples from the documentation written by
the developer, executes the library driven by the examples, gathers
run-time information, and generates a declaration file based on this
information. To evaluate the tool, 244 declaration files were generated and 
compared with the declaration file provided on DefinitelyTyped.
33 files out of 244 had no differences.
% but what about the remaining generated files
\end{abstract}
